---
title: "Binomial Vignettes"
author: "Tristan Wells"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Binomial Package Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(binomial)
```


## Binomial Variable

This package contains functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

## Identifying "trials", "prob", and "success"

The first step is to identify the probability (prob), the number of trials (trials), and the number of successes (success).

From here, you can calculate the binomial mean, mode, variance, skewness, and kurtosis using the "binomial" package as such:

```{r}
trials = 10
prob = 0.3

binmean <- bin_mean(trials, prob)
binmean
```

note that the number of trials (trials) must be postive integers, 
prob must be between 0 and 1, and success must be a positive integer less than or equal to trials.

## Calculating the Binomial Distribution

With the function "bin_distribution", you can create a list containing the binomial distribution of trials and probability

```{r}
bindis_list <- bin_distribution(trials, prob)
bindis_list
```

## Calculating the cumulative binomial distribution

with bin_cumulative, you can calulate the cumulative value of success given a probability and number of trials. 

```{r}
bincum <- bin_cumulative(trials, prob)
bincum
```


## Binomial variable

the bin_variable function will return a binomial random variable object, given a number of trials, and probability. It will provide statistics for each set of inputs. 


## n choose k

the bin_choose function will caculate the number of combinations in which k successes can occur in n trials.

## Plots

The functions plot.bincum and plot.binvar can provide plots of the list values given for bin_cumulative and bin_variable.
```{r, fig.show = "hold"}
bincum <- bin_cumulative(trials, prob)
bincum
plot(bincum)
```


> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
